Learning Network Size while Training with ShrinkNets

### 2018-02-09 paper/ICML/evaluation.tex
First part of the draft of the evaluation

\subsection{Core evaluation (CHANGE\_MY\_NAME)}

To show the versatility of our aproach we evaluate both on two very different
scenario

\subsubsection{\texttt{CIFAR10} dataset}

\gl{Cite and describe the dataset}

@@

We assume no prior knowledge on the optimal batch size, learning rate,
$\lambda$ or weight decay ($\lambda_2$). This is why, we randomly sample them
from a range of reasonable values (\gl{should we make them explicit ?}).
For each of the models we trained, we pick the epoch with the best validation
accuracy and report the corresponding testing accuracy. For each model, we also
measure the total size, in number of floating point parameters, excluding the
\textit{Switch Layers} because as we saw in section \gl{REFERENCE\_ME}, we can
get rid of them when training is done.

@@

We followed the same procedure 
\gl{Cite and describe the dataset}

We try to fit

@@

We showed in the previous section that \textit{ShrinkNets} were able to find
more or at least as efficient as \textit{Static Networks}. In this experiment we
want to determine the perf

>>>>

The goal of our evaluation is to show two main properties of
\textit{ShrinkNets}: they are exploring the space of possible sizes in a "smart"
way, and that as a result we obtain the smaller or equal size than
\textit{Static Networks}. We will then evaluate the performance benefits implied
by these gains in size.

\subsection{Datasets and Setup}

\subsubsection{\texttt{CIFAR10}}

Previous attempt at solving this problem focus on simple datasets and simple
architectures (limited to Fully connected). We believe that self-resizing
network really matter for problems where the architecture you need to solve them
involve so many layers that it is impractical to explore the space of possible
sizes. We considered ImageNet but the time required to train models is so long
that it would have not been possible to train enough and get statistically
significant results. This is why we picked \texttt{CIFAR10} [ref]. It is an
image classification dataset containing $60000$ color images $(3 \times 32
\times 32)$, belonging to $10$ different classes.

@@

We assume no prior knowledge on the optimal batch size, learning rate,
$\lambda$ or weight decay ($\lambda_2$). This is why, we randomly sample them
from a range of reasonable values (\gl{should we make them explicit ?}).
Training is done using our library, based on \texttt{PyTorch} [ref], that
support dynamically resized layers. We train the network using gradient descent
and \textit{Adam} optimizer [ref]. We start with the learning rate sampled
randomly and every $5$ epochs of non improvement in validation accuracy we
divide the learning rate by $10$. We stop training after $400$ epochs or when
the learning rate is under $10^{-7}$ whichever comes first. \gl{Should I also
  give the details about the removal strategy we used and the $\gamma$ and
  threshold I used ? because this is clearly getting boring}
For each of the models we trained, we pick the epoch with the best validation
accuracy and report the corresponding testing accuracy. For each model, we also
measure the total size, in number of floating point parameters, excluding the
\textit{Switch Layers} because as we saw in section \gl{REFERENCE\_ME}, we can
get rid of them when training is done.

@@

Our second dataset we will evaluate on is \texttt{COVERTYPE} [ref]. \gl{TODO
  rephrase the description taken from the UCI website} We picked
this one for couple of reasons. First it is simply enough that we can reach good
accuracy with small models. This important because we want to show that
\textit{ShrinkNets} find sizes as good as \textit{Static Networks}, even if we
are sampling the entire space of possible sizes. The second reason is that [ref]
are also doing their evaluation on this dataset, which allow us to compare the
results obtained by the two methods.

The only difference in terms of setup are minimal. We use the same architecture
as [ref], i.e. three layers Fully Connected neural network with  no
\textit{Dropout} [ref] nor \textit{BatchNorm} [ref]. \gl{Should we say here that we
  don't expect Dropout to work here ? I could write an entire paragraph about it
  if needed}. In this case for the \textit{Static Networks}, we sample
independently sizes of the three different layers to explore all possible
architectures.

\gl{Todo for me: explain how I select the best epoch to get rid of the outliers}

\subsection{Intepretation of the result of random search}

\gl{TODO draw conclusions from the plots}:
\begin{itemize}
  \item Pareto frontier better or as good, even when we sample the entire search
    space
  \item Static NEts are much more spread in terms of size for a given accuracy
    while shrinknets are smarter and always lie close to the frontier (I am
    changing the way I select the best epoch so the outliers in the COVER
    dataset will go away in the next version of the plot)
  \item We reach as good or better accuracies than normal networks
\end{itemize}

@@

We showed in the previous section that \textit{ShrinkNets} were able to find
more or at least as efficient as \textit{Static Networks}. In this experiment we
want to determine benefits of the smaller size we get.

For some applications, the absolute best accuracy is not something desirable if
it implies having enormous models. This observation motivates our methodology:
for a given target accuracy that you want your model to achieve, we pick the
smallest that satisfy the constraint. For both \textit{ShrinkNets} and
\textit{Static Networks} we measure multiple metrics and compute the ratio
between the two. The metrics are interested in are: the final model size (in
number of parameters) and inference speed on CPU and GPU for small batch sizes
($1$ input) and large batch sizes (depend on the dataset and hardware).
